DCM_investigation

### 2020-12-21 article_figures_ARTHUR_CAPET.Rmd
update markdown for figs

## Second option 
isoPARb <- function(depth, PAR){
  require(pracma)
  # Intended for Casted DF
  if (FilterForPAR(depth,PAR)){
    out    <- try_default({
    d <- depth[which( !is.na(depth) & PAR>0.1  )]
    P <- PAR[which( !is.na(depth) & PAR>0.1  )]
    m <<-nls2(PAR ~ Att_2band(depth,PAR0,ks0,kl0),
           data = data.frame(depth=depth, PAR=PAR),
           start = p2b_start, 
           lower = p2b_lower,
           upper = p2b_upper,
           algorithm = "port", 
           control = list(maxiter= 1000)
           )
    mcoef  <<- coef(m)
    PAR0   <-mcoef[1]
    PARcon <- predict(m,data.frame(depth=seq(1,200)))    
    z100 <- interp1(PARcon,seq(1,200), PAR0/100) 
      return(c(z100,PAR0))},
      DefOut_isoPAR)
  }else{
    out <- DefOut_isoPAR
  }
  return(out)
}

@@

```{r Fig9, fig.width=8, fig.height=6}
grid.arrange(bigplot1+scale_x_reverse(),
             bigplot2+scale_x_reverse(), nrow=1)
```

@@

ggplot(tmp_zmax, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
          scale_y_reverse(breaks = seq(100,0,-10), minor_breaks = NULL) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab('[m]')+theme_bw()+coord_cartesian(ylim=c(100,0))+
  #scale_y_reverse()+
    scale_color_brewer(aesthetics = c("colour", "fill"),
                       type = qual ,
                       palette=MyPal,
                       name="Depth Horizons", 
                       labels=list(TeX('$z_{MLD}$'),
                                TeX('$z_{DCM}$'),
                                TeX('$z_{low}$'),
                                TeX('$z_{50,bottom}$'),
                                TeX('$z_{50,top}$'),
                                TeX('$z_{\\mathrm{PAR}\\,1%}$')))
```

@@

ggplot(tmp_sig, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
  theme_bw()+
  theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
  ylab('[kg/m3]')+coord_cartesian(ylim=c(16,10))+scale_y_reverse()+
      scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
                       name="Density Horizons", 
                       labels=list(TeX('$\\sigma_{MLD}$'),
                                TeX('$\\sigma_{DCM}$'),
                                TeX('$\\sigma_{low}$'),
                                TeX('$\\sigma_{50,bottom}$'),
                                TeX('$\\sigma_{50,top}$'),
                                TeX('$\\sigma_{\\mathrm{PAR}\\,1%}$')))

@@

@@

```{r Review Fig light}

tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1','dcm_or_not','year'))

@@

relative_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
                              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
theme_bw()+
  theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
  ylab('% of Incoming PAR') +  scale_y_continuous(trans = 'log10') +
  scale_color_manual(aesthetics = c("colour", "fill"),
                         values = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E", "#E6AB02"),
                       name="ISO Horizons", 
                       labels=list(TeX('$\\ISO_{MLD}$'),
                                   TeX('$\\ISO_{DCM}$'),
                                   TeX('$\\ISO_{low}$'),
                                   TeX('$\\ISO_{50,bottom}$'),
                                   TeX('$\\ISO_{50,top}$'),
                                   TeX('$\\ISO_{1%}$')))

relative_light

#absolute light
tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOaMLD','ISOaMAX','ISOalow','ISOa90B','ISOa90T','dcm_or_not','year','shape'))

@@

absolute_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
  theme_bw()+
  theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
  scale_y_continuous(trans = 'log10') +
  ylab(TeX('$\\mu molQuanta\\,m^{-2}\\,s^{-1}]$')) +
  scale_color_manual(aesthetics = c("colour", "fill"),
                     values = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E"),
                       name="ISO Horizons", 
                       labels=list(TeX('$\\ISO_{MLD}$'),
                                   TeX('$\\ISO_{DCM}$'),
                                TeX('$\\ISO_{low}$'),
                                TeX('$\\ISO_{50,bottom}$'),
                                TeX('$\\ISO_{50,top}$')))

@@

@@

```{r Fig8}
require(reshape2)
tmp_part <- melt(subset(tmp_fitco, select = c('month','year','RaMLD_chla','DCMratio')), id.vars=c('month','year'))
#,'visible_ratio'

ggplot(tmp_part, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
        scale_y_continuous(breaks = seq(0,100,10), minor_breaks = NULL) +
    geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab('[%]')+theme_bw()+
  scale_color_brewer(name='Part of tot. Chl:',
                     labels=c('above MLD','within 5m of DCM','above optical depth'),
                     aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)#+ylim(c(0,100))

@@

```{r Fig7}
require(reshape2)
tmp_conc1<-subset(tmp_fitco, select = c('total_chla','chla_surf','chla_dcm','month','year','dcm_or_not'))

@@

  ggplot(tmp_conc, aes(x=month, fill=variable, color=variable)) +
      geom_smooth(aes(y=value),stat = 'summary',
  #              fun.data = median_hilow,
                fun.data = mean_cl_boot,
                fun.args = list(conf.int = 0.95), alpha=0.5)+
          scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
      geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2)+
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ylab('[mg/m3]')+theme_bw()+coord_cartesian(ylim=c(0,3.5))+
    scale_color_brewer(aesthetics = c("colour", "fill"),type = qual,
                       palette=MyPal, 
                       name="Chla concentrations",
                       labels=c("Average","Surface","DCM"))
```

@@

```{r ratio_spatial2b}

@@

discfigb1<-ggplot(ddd, 
       aes(x = month, y = ratio, color=cutlon, fill=cutlon))+
  theme_bw()+
   geom_boxplot(aes(group= bibi),
                alpha=0.2, notch = TRUE, varwidth = FALSE, position='dodge2')+
  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
  scale_color_brewer(aesthetics = c("colour", "fill"),
                     type = qual ,palette=MyPal, name="Longitude", labels=c('West','East')) +
  ylab(TeX('$\\sigma_{DCM}/\\sigma_{MLD,max}$'))

@@

```{r Fig4,fig.width=8,fig.height=8}

@@

P_years_depth <- ggplot(subset(tmp_zmax, variable !="Zdemi"), aes(x=month, fill=variable, color=variable)) +
    geom_line(data=subset(tmp_zmaxA, variable !="Zdemi"),aes(y=value),alpha =1, size=0.5, linetype=2)+
      geom_smooth(aes(y=value, group=variable),
                  stat = 'summary',
                  fun.data = mean_cl_boot,
                  fun.args = list(conf.int = 0.95), 
                  alpha=0.2, linetype=0)+
  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
  ylab('[m]')+theme_bw()+
  coord_cartesian(ylim=c(90,0), expand = FALSE)+scale_y_reverse()+
  scale_color_brewer(aesthetics = c("colour", "fill"),
                       type = qual ,
                       palette=MyPal,
                       name="Depth Horizons", 
                       labels=list(TeX('$z_{MLD}$'),
                                TeX('$z_{DCM}$'),
                                TeX('$z_{low}$'),
                                TeX('$z_{50,bottom}$'),
                                TeX('$z_{50,top}$'),
                                TeX('$z_{\\mathrm{PAR}\\,1%}$')))+
#  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal, name='')+
  facet_grid(.~year)+
  theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+
  guides(colour = guide_legend(nrow = 1))

@@

P_years_sig <-ggplot(tmp_sig, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_sigA,aes(y=value),alpha =1, size=0.5, linetype=2)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), 
                  alpha=0.2, linetype=0)+
  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
  ylab('[kg/m3]')+theme_bw()+
  coord_cartesian(ylim=c(10,16), expand = FALSE)+
  scale_y_reverse()+
  #scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
                       name="Density Horizons", 
                       labels=list(TeX('$\\sigma_{MLD}$'),
                                TeX('$\\sigma_{DCM}$'),
                                TeX('$\\sigma_{low}$'),
                                TeX('$\\sigma_{50,bottom}$'),
                                TeX('$\\sigma_{50,top}$'),
                                TeX('$\\sigma_{\\mathrm{PAR}\\,1%}$')))+
  facet_grid(.~year)+
  theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+
          guides(colour = guide_legend(nrow = 1))

@@

@@

P_years_part <-ggplot(tmp_part, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_partA,aes(y=value),alpha =1, size=0.5, linetype=2)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args =  list(conf.int = 0.95), 
                  alpha=0.2, linetype=0)+
  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
  ylab('[%]')+theme_bw()+coord_cartesian(ylim=c(0,100), expand = FALSE)+
  scale_color_brewer(name='Part of tot. Chl:',
                     labels=c('above MLD','within 5m of DCM','above optical depth'),
                     aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  facet_grid(.~year)+theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+ guides(colour = guide_legend(nrow = 1))

@@

P_years_conc <-ggplot(tmp_conc, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_concA,aes(y=value),alpha =1, size=0.5, linetype=2)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), 
                  alpha=0.2, linetype=0)+
  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
  ylab('[mg/m3]')+theme_bw()+coord_cartesian(ylim=c(0,3), expand = FALSE)+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  facet_grid(.~year)+scale_color_brewer(aesthetics = c("colour", "fill"),type = qual,
                       palette=MyPal, 
                       name="Chla concentrations",
                       labels=c("Average","Surface","DCM"))+
  facet_grid(.~year)+theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+ guides(colour = guide_legend(nrow = 1))

@@

```{r Fig11, fig.height=12, fig.width=10}
grid.arrange(P_years_depth,
             P_years_sig+theme( strip.background = element_blank(),strip.text.x = element_blank()), 
             P_years_part+theme( strip.background = element_blank(),strip.text.x = element_blank()),
             P_years_conc+theme( strip.background = element_blank(),strip.text.x = element_blank()),
             ncol=1)

>>>>

## Second option 
isoPARb <- function(depth, PAR){
  require(pracma)
  # Intended for Casted DF
  if (FilterForPAR(depth,PAR)){
    out    <- try_default({
    d <- depth[which( !is.na(depth) & PAR>0.1  )]
    P <- PAR[which( !is.na(depth) & PAR>0.1  )]
    m <<-nls(PAR ~ Att_2band(depth,PAR0,ks0,kl0),
           data = data.frame(depth=depth, PAR=PAR),
           start = p2b_start, 
           lower = p2b_lower,
           upper = p2b_upper,
           algorithm = "port", 
           control = list(maxiter= 1000)
           )
    mcoef  <<- coef(m)
    PAR0   <-mcoef[1]
    PARcon <- predict(m,data.frame(depth=seq(1,200)))    
    z100 <- interp1(PARcon,seq(1,200), PAR0/100) 
      return(c(z100,PAR0))},
      DefOut_isoPAR)
  }else{
    out <- DefOut_isoPAR
  }
  return(out)
}

@@

```{r Fig10, fig.width=8, fig.height=6}
grid.arrange(bigplot1+scale_x_reverse(),
             bigplot2+scale_x_reverse(), nrow=1)
```

@@

depthplot <- ggplot(tmp_zmax, aes(x=month)) +
    geom_smooth(aes(y=value, fill=variable, color=variable),stat = 'summary',
#              fun.data = median_hilow,
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, fill=variable, color=variable, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), limits = c(0.5,12.5), expand = c(0, 0)) +
          scale_y_reverse(breaks = seq(100,0,-10), minor_breaks = NULL) +
  ylab('[m]')+theme_bw()+coord_cartesian(ylim=c(100,0))+
    theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
  #scale_y_reverse()+
    scale_color_brewer(aesthetics = c("colour", "fill"),
                       type = qual ,
                       palette=MyPal,
                       name="Depth Horizons", 
                       labels=list(TeX('$z_{MLD}$'),
                                TeX('$z_{DCM}$'),
                                TeX('$z_{low}$'),
                                TeX('$z_{50,bottom}$'),
                                TeX('$z_{50,top}$'),
                                TeX('$z_{\\mathrm{PAR}\\,1%}$')))

depthplot
```

@@

densplot <- ggplot(tmp_sig, aes(x=month)) +
    geom_smooth(aes(y=value, fill=variable, color=variable),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, fill=variable, color=variable,group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), expand = c(1, 1)*0.01) +
  theme_bw()+
  theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
  ylab(TeX('$\\left[kg\\,m^{-3}\\right]$$'))+coord_cartesian(ylim=c(16,10))+scale_y_reverse()+
      scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
                       name="Density Horizons", 
                       labels=list(TeX('$\\sigma_{MLD}$'),
                                TeX('$\\sigma_{DCM}$'),
                                TeX('$\\sigma_{low}$'),
                                TeX('$\\sigma_{50,bottom}$'),
                                TeX('$\\sigma_{50,top}$'),
                                TeX('$\\sigma_{\\mathrm{PAR}\\,1%}$')))

@@

densplot

@@

```{r Review Fig light}
tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1','dcm_or_not','year'))

@@

relative_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
                              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), expand = c(1, 1)*0.01) +
theme_bw()+
  theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
  ylab('% of Incoming PAR') +  scale_y_continuous(trans = 'log10') +
  scale_color_manual(aesthetics = c("colour", "fill"),
                         values = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E", "#E6AB02"),
                       name="ISO Horizons", 
                       labels=list(TeX('$\\ISO_{MLD}$'),
                                   TeX('$\\ISO_{DCM}$'),
                                   TeX('$\\ISO_{low}$'),
                                   TeX('$\\ISO_{50,bottom}$'),
                                   TeX('$\\ISO_{50,top}$'),
                                   TeX('$\\ISO_{1%}$')))

relative_light
```

```{r Fig7}
#absolute light
tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOaMLD','ISOaMAX','ISOalow','ISOa90B','ISOa90T','dcm_or_not','year','shape'))

@@

absolute_light <- ggplot(tmp_iso, aes(x=month)) +
    geom_smooth(aes(y=value, fill=variable, color=variable),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, fill=variable, color=variable, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), expand = c(1, 1)*0.01) +
  theme_bw()+
  theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
  scale_y_continuous(trans = 'log10') +
  ylab(TeX('$\\left[\\mu mol\\,photons\\,m^{-2}\\,s^{-1}\\right]$')) +
  scale_color_manual(aesthetics = c("colour", "fill"),
                     values = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E"),
                       name="PAR Horizons",
                      labels=list(TeX('$\\mathrm{PAR$_{MLD}$'),
                                   TeX('$\\mathrm{PAR}_{DCM}$'),
                                   TeX('$\\mathrm{PAR}_{low}$'),
                                   TeX('$\\mathrm{PAR}_{50,bottom}$'),
                                   TeX('$\\mathrm{PAR}_{50,top}$')))

@@

```{r FigR5, fig.width=10, fig.height=10}
gA <- ggplotGrob(depthplot+
  geom_text(data=data.frame(x=1, y=0, label='a)'), aes(x=x, y=y, label=label), color='black', fill='black', size=5))
gB <- ggplotGrob(densplot+
  geom_text(data=data.frame(x=1, y=10, label='b)'), aes(x=x, y=y, label=label), color='black', fill='black', size=5))
gC <- ggplotGrob(absolute_light+
  geom_text(data=data.frame(x=1, y=300, label='c)'), aes(x=x, y=y, label=label), color='black', fill='black', size=5))
grid::grid.newpage()
grid::grid.draw(rbind(gA, gB, gC))
```

@@

```{r Fig9}
require(reshape2)
tmp_part <- melt(subset(tmp_fitco, select = c('month','year','RaMLD_chla','DCMratio')), id.vars=c('month','year'))
#,'visible_ratio'

partplot <- ggplot(tmp_part, aes(x=month)) +
    geom_smooth(aes(y=value, fill=variable, color=variable),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), expand = c(1,1)*0.01) +
    theme_bw()+
  theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
        scale_y_continuous(breaks = seq(0,100,10), minor_breaks = NULL) +
    geom_boxplot(aes(y=value, fill=variable, color=variable, group=interaction(month,variable)), alpha=0.2)+
  ylab('[%]')+
  scale_color_brewer(name='Part of tot. Chl:',
                     labels=c('above MLD','within 5m of DCM','above optical depth'),
                     aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)#+ylim(c(0,100))

partplot

@@

```{r Fig8}
require(reshape2)
tmp_conc1<-subset(tmp_fitco, select = c('total_chla','chla_surf','chla_dcm','month','year','dcm_or_not'))

@@

concplot<-  ggplot(tmp_conc, aes(x=month)) +
      geom_smooth(aes(y=value, fill=variable, color=variable),stat = 'summary',
  #              fun.data = median_hilow,
                fun.data = mean_cl_boot,
                fun.args = list(conf.int = 0.95), alpha=0.5)+
          scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), expand = c(0, 0)) +
        theme_bw()+
  theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
      geom_boxplot(aes(y=value, fill=variable, color=variable, group=interaction(month,variable)), alpha=0.2)+
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ylab(TeX('$\\left[mg\\,m^{-3}\\right]$$'))+coord_cartesian(ylim=c(0,2.5))+
    scale_color_manual(aesthetics = c("colour", "fill"),
                     values = c("#1B9E77", "#7570B3","#D95F02"),#,  "#E7298A", "#66A61E"),
                       name="Chla concentration", 
                       labels=c("Total (scaled)","Surface","DCM"))

concplot
```

```{r FigR6, fig.width=10, fig.height=6}
gA <- ggplotGrob(concplot+
  geom_text(data=data.frame(x=1, y=2.5, label='a)'), aes(x=x, y=y, label=label), color='black', fill='black', size=5))
gB <- ggplotGrob(partplot+
  geom_text(data=data.frame(x=1, y=100, label='b)'), aes(x=x, y=y, label=label), color='black', fill='black', size=5))

grid::grid.newpage()
grid::grid.draw(rbind(gA,gB))
```

@@

```{r Fig11, fig.width=10, fig.height=3}

@@

discfigb1<-ggplot(ddd, 
       aes(x = month, y = ratio, color=cutlon, fill=cutlon))+
   geom_boxplot(aes(group= bibi),
                alpha=0.2, notch = TRUE, varwidth = FALSE, position='dodge2')+
  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), expand = c(1,1)*0.01)+
          theme_bw()+
  theme(panel.grid.minor.x = element_line(colour = "grey"),
        panel.grid.major.x = element_line(colour = "white")) +
  scale_color_brewer(aesthetics = c("colour", "fill"),
                     type = qual ,palette=MyPal, name="Longitude", labels=c('West','East')) +
  ylab(TeX('$\\sigma_{DCM}/\\sigma_{MLD,max}$'))

@@

```{r Fig4,fig.width=8,fig.height=5}

@@

P_years_depth <- ggplot(subset(tmp_zmax, variable !="Zdemi"), aes(x=month, fill=variable, color=variable)) +
    geom_line(data=subset(tmp_zmaxA, variable !="Zdemi"),aes(y=value),alpha =1, size=0.5, linetype=2)+
      geom_smooth(aes(y=value, group=variable),
                  stat = 'summary',
                  fun.data = mean_cl_boot,
                  fun.args = list(conf.int = 0.95), 
                  alpha=0.2, linetype=0)+
  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5), expand = c(0,0))+
  ylab('[m]')+theme_bw()+
  coord_cartesian(ylim=c(90,0), expand = FALSE)+scale_y_reverse()+
  scale_color_brewer(aesthetics = c("colour", "fill"),
                       type = qual ,
                       palette=MyPal,
                       name="Depth Horizons : ", 
                       labels=list(TeX('$z_{MLD}$'),
                                TeX('$z_{DCM}$'),
                                TeX('$z_{low}$'),
                                TeX('$z_{50,bottom}$'),
                                TeX('$z_{50,top}$'),
                                TeX('$z_{\\mathrm{PAR}\\,1%}$')))+
#  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal, name='')+
  facet_grid(.~year)+
  theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+
  guides(colour = guide_legend(nrow = 1))

@@

P_years_sig <-ggplot(tmp_sig, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_sigA,aes(y=value),alpha =1, size=0.5, linetype=2)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), 
                  alpha=0.2, linetype=0)+
  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
  ylab(TeX('$\\left[kg\\,m^{-3}\\right]$$'))+
  coord_cartesian(ylim=c(16,10), expand = FALSE)+
  theme_bw()+
  #scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
                       name="Density Horizons : ", 
                       labels=list(TeX('$\\sigma_{MLD}$'),
                                TeX('$\\sigma_{DCM}$'),
                                TeX('$\\sigma_{low}$'),
                                TeX('$\\sigma_{50,bottom}$'),
                                TeX('$\\sigma_{50,top}$'),
                                TeX('$\\sigma_{\\mathrm{PAR}\\,1%}$')))+
  facet_grid(.~year)+
  theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+
          guides(colour = guide_legend(nrow = 1))

@@

```{r inter_light, include=FALSE}
#absolute light
tmp_isoC<- dcast(tmp_iso,formula = month~variable, fun.aggregate = median, na.rm=TRUE)
tmp_isoA<-melt(tmp_isoC, id.vars=c('month'))

P_years_iso <-ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_isoA,aes(y=value),alpha =1, size=0.5, linetype=2)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), 
                  alpha=0.2, linetype=0)+
  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
  ylab(TeX('$\\left[\\mu mol\\,photons\\,m^{-2}\\,s^{-1}\\right]$'))+theme_bw()+
    scale_y_continuous(trans = 'log10') +
  #scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
                       name="PAR Horizons : ", 
                       labels=list(TeX('$\\mathrm{PAR$_{MLD}$'),
                                   TeX('$\\mathrm{PAR}_{DCM}$'),
                                   TeX('$\\mathrm{PAR}_{low}$'),
                                   TeX('$\\mathrm{PAR}_{50,bottom}$'),
                                   TeX('$\\mathrm{PAR}_{50,top}$')))+
  facet_grid(.~year)+
  theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+
          guides(colour = guide_legend(nrow = 1))
P_years_iso

@@

P_years_part <-ggplot(tmp_part, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_partA,aes(y=value),alpha =1, size=0.5, linetype=2)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args =  list(conf.int = 0.95), 
                  alpha=0.2, linetype=0)+
  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5), expand = c(0,0))+
  ylab('[%]')+theme_bw()+coord_cartesian(ylim=c(0,100), expand = FALSE)+
  scale_color_brewer(name='Part of tot. Chl : ',
                     labels=c('above MLD','within 5m of DCM','above optical depth'),
                     aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  facet_grid(.~year)+theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+ guides(colour = guide_legend(nrow = 1))

@@

P_years_conc <-ggplot(tmp_conc, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_concA,aes(y=value),alpha =1, size=0.5, linetype=2)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), 
                  alpha=0.3, linetype=0)+
  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5), expand = c(0,0))+
  ylab('[mg/m3]')+theme_bw()+coord_cartesian(ylim=c(0,3), expand = FALSE)+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  facet_grid(.~year)+scale_color_brewer(aesthetics = c("colour", "fill"),type = qual,
                       palette=MyPal, 
                       name="Chla concentrations : ",
                       labels=c("Total (scaled)","Surface","DCM"))+
  facet_grid(.~year)+theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+ guides(colour = guide_legend(nrow = 1))

@@

```{r Fig12, fig.height=12, fig.width=10}
grid.arrange(P_years_depth,
             P_years_sig+theme( strip.background = element_blank(),strip.text.x = element_blank()), 
             P_years_iso+theme( strip.background = element_blank(),strip.text.x = element_blank()), 
             P_years_part+theme( strip.background = element_blank(),strip.text.x = element_blank()),
             P_years_conc+theme( strip.background = element_blank(),strip.text.x = element_blank()),
             ncol=1)
